\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm, right=1cm, top=0.5cm, bottom=1.5cm]{geometry}
\usepackage{xcolor}

\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% -- COLORS --
\definecolor{primaryblue}{HTML}{007BFF}
\definecolor{darktext}{HTML}{000000}
\definecolor{graytext}{HTML}{555555}

% -- FONTS --
\renewcommand{\familydefault}{\sfdefault}

% -- HYPERLINKS --
\hypersetup{
    colorlinks=true,
    linkcolor=primaryblue,
    filecolor=primaryblue,
    urlcolor=primaryblue,
    citecolor=primaryblue
}

% -- SECTION FORMATTING --
% \titlespacing*{command}{left}{before-sep}{after-sep}
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}
  {0em}
  {}
  [{\color{black}\titlerule[1.5pt]}]

\titlespacing*{\section}{0pt}{12pt}{8pt}

% -- PAGE STYLE --
\pagestyle{empty} % REMOVES PAGE NUMBERS

% -- CUSTOM COMMANDS --
\newcommand{\entrytitle}[1]{\textbf{\large #1}}
\newcommand{\entrysubtitle}[1]{{\color{primaryblue}\textbf{#1}}}
\newcommand{\entrymeta}[1]{{\small\color{graytext} #1}}

\begin{document}

% ================= HEADER (CENTERED) =================
\begin{center}
    {\fontsize{24}{30}\bfseries\uppercase{Sarveesh Kaarthic}}\\[0.2cm]
    
    {\small
    +91 9360181997 \quad | \quad
    \href{mailto:sarveeshkaarthic05@gmail.com}{sarveeshkaarthic05@gmail.com} \quad | \quad
    \href{https://www.linkedin.com/in/sarveesh-kaarthic-ramesh-kannan-750569380}{Sarveesh Kaarthic} \quad | \quad
    \href{https://github.com/SarveeshK}{SarveeshK}
    }
\end{center}

\vspace{0.4cm}

% ================= CONTENT COLUMNS =================
\noindent
\begin{minipage}[t]{0.60\textwidth} % LEFT COLUMN (60%)
    
    % --- PROFESSIONAL SUMMARY ---
    \section*{Professional Summary}
    Results-oriented \textbf{Full Stack Developer} specializing in building scalable digital solutions. Expert in leveraging \textbf{Artificial Intelligence} to accelerate development cycles and optimize backend logic. Committed to continuous learning and applying modern web technologies to solve complex real-world challenges.

    \vspace{0.4cm}

    % --- EXPERIENCE ---
    \section*{Professional Experience}
    
    % Exp 1
    \entrytitle{Python Development Intern} \\
    \entrysubtitle{Infotact Solutions} \\
    \entrymeta{01/2026 -- Present \quad | \quad Remote} \\
    \begin{itemize}[leftmargin=1.5em, nosep, topsep=4pt]
        \item Executing rapid-prototyping sprints focused on advanced Python backend architecture and algorithmic optimization.
        \item Optimized code modularity and algorithms, reducing data processing time by \textbf{30\%} using AI-assisted workflows.
    \end{itemize}
    \vspace{8pt}

    % Exp 2
    \entrytitle{Web Developer Intern} \\
    \entrysubtitle{Macs Solutions} \\
    \entrymeta{12/2025 -- 01/2026 \quad | \quad Erode} \\
    \begin{itemize}[leftmargin=1.5em, nosep, topsep=4pt]
        \item Architected and deployed \textbf{"Work Hub - CES"}, a workflow system used by community members to manage daily operations.
        \item Reduced administrative task allocation time by \textbf{40\%} through the implementation of an automated role-based dashboard.
        \item Integrated AI-driven code assistants to accelerate feature delivery, completing the project ahead of schedule.
    \end{itemize}
    \vspace{8pt}

    % Exp 3
    \entrytitle{Full Stack with AI Intern} \\
    \entrysubtitle{Nuvai AI Solutions} \\
    \entrymeta{07/2025 \quad | \quad Bengaluru} \\
    \begin{itemize}[leftmargin=1.5em, nosep, topsep=4pt]
        \item Developed core modules for \textbf{Docky} (SaaS), optimizing frontend performance to handle simultaneous document uploads.
        \item Enhanced file handling system, improving upload speeds by \textbf{25\%} and achieving high system stability.
    \end{itemize}

    % --- EDUCATION ---
    \section*{Education}
    \entrytitle{BE (Electronics and Communication)} \\
    \entrysubtitle{Government College of Engineering, Erode} \\
    \entrymeta{08/2023 -- 05/2027 \hfill \textbf{CGPA: 7.98}}
    \vspace{5pt}

    \entrytitle{Higher Secondary (HSC)} \\
    \entrysubtitle{Jaycees Matriculation Hr. Sec. School} \\
    \entrymeta{04/2022 -- 03/2023 \hfill \textbf{Percentage: 84.3\%}}
    \vspace{5pt}

    \entrytitle{Secondary School (SSLC)} \\
    \entrysubtitle{Jaycees Matriculation Hr. Sec. School} \\
    \entrymeta{04/2020 -- 03/2021 \hfill \textbf{Percentage: 100\%}}

\end{minipage}%
\hfill % Gutter space
\begin{minipage}[t]{0.36\textwidth} % RIGHT COLUMN (35%)

    % --- STRENGTHS ---
    \section*{Key Strengths}
    
    \begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=10pt]
        \item \textbf{Team Leadership} \\
        {\small Fostering collaboration and driving technical knowledge sharing.}
        
        \item \textbf{Learning Agility} \\
        {\small Rapidly adapting to new technologies and evolving development environments.}
    \end{itemize}

    % --- ACHIEVEMENTS ---
    \section*{Achievements}
    
    \begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=10pt]
        \item \textbf{Real-World Deployment} \\
        {\small Built and deployed 2 full-stack applications integrating AI tools, used by real users during internship projects.}
    \end{itemize}

    % --- SKILLS ---
    \section*{Tools \& Technologies}
    % Reduced spacing here as requested
    
    \textbf{Languages:} Python, JavaScript, TypeScript, SQL \\
    \textbf{Frameworks:} React.js, Flask \\
    \textbf{Tools:} Git, GitHub, VS Code, Render, Vercel, Netlify \\
    \textbf{AI Tools:} Cursor AI, Antigravity

    % --- INTERESTS ---
    \section*{Areas of Interest}
    
    \begin{itemize}[leftmargin=1.5em, labelsep=0.5em, itemsep=10pt]
        \item \textbf{App Development} \\
        {\small Building intuitive, user-centric web applications.}
        
        \item \textbf{AI Exploration} \\
        {\small Investigating real-world use cases for Generative AI.}
    \end{itemize}

    % --- PROJECTS ---
    \section*{Mini Projects}
    \begin{itemize}[leftmargin=0pt, label={}]
        \item \textbf{Work Hub - CES} \\
        {\small Workflow management \& Issue tracking system with RBAC for academic operations.} \\
        {\small \textbf{Tech Stack:} React, Flask, PostgreSQL}
        \vspace{6pt}
        \item \textbf{Docky SaaS} \\
        {\small Secure document management system featuring user dashboards and cloud storage.} \\
        {\small \textbf{Tech Stack:} React, Python, Cloud Storage}
    \end{itemize}

\end{minipage}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
